Prototype city generation for mobility simulation in urban typologies: a generalized framework

### 2017-12-26 manuscript/manuscript.tex
subsections on land use added

\begin{enumerate}[Step 1:]
\item Network: modify OSM network file, make it legal input to SimMobility
  \begin{enumerate}[1.]
  \item links has to be unidirectional
  \item shorten the links and add turning points
  \item maintain the attributes of each object in the network
  \end{enumerate}
\item Population Synthesis
  \begin{enumerate}[1.]
  \item Data collection: sample data, aggregate data for zones in each city
  \item Data processing: categorize sample data and get joint distribution, formatting aggregate data
  \item Apply IPF algorithm and use the weights result to draw synthetic population
  \item Assign households in each county to locations based on land use information
  \end{enumerate} 
\end{enumerate}

@@

\subsection{Estimation of origin-destination matrices}
There are three key inputs at the zonal level required for running SimMobility preday: zonal attribute data, skim matrices, and zone-zone travel time data.

>>>>

% \begin{enumerate}[Step 1:]
% \item Network: modify OSM network file, make it legal input to SimMobility
%   \begin{enumerate}[1.]
%   \item links has to be unidirectional
%   \item shorten the links and add turning points
%   \item maintain the attributes of each object in the network
%   \end{enumerate}
% \item Population Synthesis
%   \begin{enumerate}[1.]
%   \item Data collection: sample data, aggregate data for zones in each city
%   \item Data processing: categorize sample data and get joint distribution, formatting aggregate data
%   \item Apply IPF algorithm and use the weights result to draw synthetic population
%   \item Assign households in each county to locations based on land use information
%   \end{enumerate} 
% \end{enumerate}

In summary, the following are steps involving in generating a synthetic population and preparing it for mesoscopic simulation.
\begin{itemize}
\item 
\item 
\end{itemize}

@@

\subsection{Geolocation and spatial assignment}

\subsubsection{Households}
\begin{itemize}
  \item Aggregate land use categories into these: low residential ($L$), high residential ($H$), commercial ($C$), industrial ($I$), education ($E$), open land ($O$)
  \item Assign weights for households as follows:
    \begin{equation}
     HH (w_L, w_H, w_C, w_I, w_E, w_O) = (8, 10, 4, 1, 0, 0)
    \end{equation}
  \item Grid the map and assign weights to the cell $w_c^{HH}$ given its  prevailing land use category
  \item Normalize cell weights $p_{c(SAL)}^{HH}$ in each second administrative level ($SAL$)
    \begin{equation}
      p_{c(SAL)}^{HH} = \fr{w_c^{HH}}{\sum_{c \in SAL} w_c^{HH}}
    \end{equation}
  \item Number of households in each cell given by:
    \begin{equation}
     N_{HH}^{c(SAL)} = p_c^{SAL}\cdot N_{HH}^{SAL}
    \end{equation}
    where $ N_{HH}^{SAL}$ is the number of households in each $SAL$.
  \item Randomly sample to locate households in cell centroids for all $SAL$
  \end{itemize}

\subsubsection{Firms and education zones}
\begin{itemize}
  \item We obtain numbers of firms and schools in each $SAL$
  \item Assign weights as follows:
    \begin{align}
      WORK (w_L, w_H, w_C, w_I, w_E, w_O) &= (1, 2, 10, 5, 3, 1)\\
      EDU (w_L, w_H, w_C, w_I, w_E, w_O) &= (0, 0, 0, 0, 1, 0)
    \end{align}
  \item Assign weights to cells for work and education: $w_c^{WORK}$,  $w_c^{EDU}$

  \item Find $p_{c(SAL)}^{WORK}$ and $p_{c(SAL)}^{EDU}$ as before
  \item Find  $N_{WORK}^{c(SAL)}$ and $ N_{EDU}^{c(SAL)}$ as before
  \item The final outputs here are the numbers of workplaces/schools in each TAZ:
    \begin{align}
      N_{WORK}^{TAZ(SAL)} &= \sum_{c(SAL) \in TAZ(SAL)} N_{WORK}^{c(SAL)} \\
      N_{EDU}^{TAZ(SAL)} &= \sum_{c(SAL) \in TAZ(SAL)} N_{EDU}^{c(SAL)}  
    \end{align}
  \end{itemize}

\subsection{Zonal-level  estimation}
\subsubsection{Estimation of origin-destination matrices}
There are three key inputs at the zonal level required for running SimMobility preday: zonal attribute data, skim matrices, and zone-zone travel time data.
